\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-08-31 manuscript.Rmd

@@

```{r setup, include = FALSE}
library(papaja) # devtools::install_github("crsh/papaja")
library(readr)
library(readxl)
library(lavaan)
library(semPlot)
library(semTools)
library(hemp) # devtools::install_github("cddesja/hemp")
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
r_refs("r-references.bib")
```

@@

# Results

# Confirmatory Factor Analysis
# Confirmatory Factor Analysis

>>>>

  - name          : "Manuel Spitschan "
    affiliation   : "3"
    corresponding : yes   
    address       : ""
    email         : ""
    role:         
      - Data Analysis
      - Writing - Original Draft Preparation
      - Data Visualization

@@

```{r setup, include = FALSE}
library(papaja) # devtools::install_github("crsh/papaja")
library(readr)
library(readxl)
library(lavaan)
library(semPlot)
library(semTools)
library(hemp) # devtools::install_github("cddesja/hemp")
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg)
library(rsvg)
r_refs("r-references.bib")
```

@@

# Results
```{r Normality assumption EFA}
LB <- read_excel("recoded not reversed_EFA.xlsx")
LB$X1 <- NULL
KMO <- KMO(LB)

```
Sampling adequacy was investigated by Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy . The overall KMO vale for 23 items was `r printnum(KMO$MSA)` which was above the cutoff value of .50 indicating a mediocre sample [@RN1179].
# Confirmatory Factor Analysis
# Confirmatory Factor Analysis
